|

### 2024-10-28 output/seminar-slideshow.qmd
Apply canonical markdown formatting to progress

:::::::::: columns
:::::: {.column width="60%"}
```{r irt-curves}
#| fig-asp:   0.6
#| fig-width: 8

@@

::::: {.column width="40%"}
::: {.fragment fragment-index="1"}
$$
  P(Y_i = 1) = \Phi_L (a_i (\theta - b_i))
$$
:::

@@

:::::
::::::::::

@@

::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  4.6
#| fig-height: 4.6
PROB_AXIS_2D <- seq(-3, 3, by = .1)

@@

contour_plot
```
:::
:::

@@

::: columns
::: column
$$
  P(Y_1 = 1) = \Phi_L (\mathbf{a}_1^T \mathbf{\theta} + d_1)
$$

@@

::: column
\begin{matrix}
  \mathbf{\theta} =
    \begin{bmatrix}
       1 \\
      -1
    \end{bmatrix}

@@

::: fragment
$$
  \begin{align}
    P(Y_1 = 1) &= \Phi_L \left([1, 0.5]
      \begin{bmatrix}
         1 \\
        -1
      \end{bmatrix}
      -0.5 \right) \\
      &= \Phi_L \left(1 · 1 + 0.5 · (-1) -0.5 \right) \\
      &= \Phi_L \left(1 -0.5 -0.5 \right) = \Phi_L \left(0 \right) \\
      &= \frac{1}{1 + e^{-0}} = \frac{1}{1 + 1} = \frac{1}{2} = 0.5
  \end{align}
$$
:::
:::
:::

@@

> \[...\] the most reasonable point to use in defining the [multidimensional difficulty] for an item in the multidimensional space is the point where the item is most discriminating.

@@

:::: columns
::: column
```{r mid-representation}
#| fig-height: 8
#| fig-width:  8

@@

::: column
::: fragment
$$
  cos \, \mathbf{\alpha}_i = \frac{\mathbf{a}_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}}
$$
:::

@@

::: fragment
$$
  MID_i = \begin{Bmatrix}
    \frac{-d_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}} \\
    \frac{\mathbf{a}_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}}
  \end{Bmatrix}
$$
:::
:::
::::

@@

:::: {.columns .fragment}

::: column
<br>

@@

::: column
```{r mdisc-item}
#| fig-width:  4
#| fig-height: 4
mirt_item_coords |>
  arrange(desc(item))   |> # To plot them in reverse order
  ggplot(
    aes(
      0, 0,
      xend = end_transf_1 - origin_transf_1,
      yend = end_transf_2 - origin_transf_2,
      color = factor(item), fill = factor(item)
    ),
  )                                                  +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
  geom_hline(yintercept = 0, linewidth = LINE_WIDTH) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  ) +
  scale_x_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_y_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_color_manual(values = unname(PALETTE_BLUE["normal"]), guide = NULL) +
  coord_fixed(expand = FALSE, clip = "on")           +
  theme(
    axis.line        = element_blank(),
    panel.grid.major = element_line(
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```
:::
::::

>>>>

::::::::::: columns
:::::: {.column width="60%"}
```{r irt-curves}
#| fig-asp:   0.6
#| fig-width: 8

@@

:::::: {.column width="40%"}
::: {.fragment fragment-index="1"}
$$
  P(Y_i = 1) = \Phi_L (a_i (\theta - b_i))
$$
:::

@@

<br>
::::::
:::::::::::

@@

::::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  4.6
#| fig-height: 4.6
PROB_AXIS_2D <- seq(-3, 3, by = .1)

@@

contour_plot
```
:::
:::::

@@

:::::: columns
::: column
$$
  P(Y_1 = 1) = \Phi_L (\mathbf{a}_1^T \mathbf{\theta} + d_1)
$$

@@

:::: column
\begin{matrix}
  \mathbf{\theta} =
    \begin{bmatrix}
       1 \\
      -1
    \end{bmatrix}

@@

::: fragment
$$
  \begin{align}
    P(Y_1 = 1) &= \Phi_L \left([1, 0.5]
      \begin{bmatrix}
         1 \\
        -1
      \end{bmatrix}
      -0.5 \right) \\
      &= \Phi_L \left(1 · 1 + 0.5 · (-1) -0.5 \right) \\
      &= \Phi_L \left(1 -0.5 -0.5 \right) = \Phi_L \left(0 \right) \\
      &= \frac{1}{1 + e^{-0}} = \frac{1}{1 + 1} = \frac{1}{2} = 0.5
  \end{align}
$$
:::
::::
::::::

@@

> \[...\] the most reasonable point to use in defining the \[multidimensional difficulty\] for an item in the multidimensional space is the point where the item is most discriminating.

@@

::::::: columns
::: column
```{r mid-representation}
#| fig-height: 8
#| fig-width:  8

@@

::::: column
::: fragment
$$
  cos \, \mathbf{\alpha}_i = \frac{\mathbf{a}_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}}
$$
:::

@@

::: fragment
$$
  MID_i = \begin{Bmatrix}
    \frac{-d_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}} \\
    \frac{\mathbf{a}_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}}
  \end{Bmatrix}
$$
:::
:::::
:::::::

@@

::::: {.columns .fragment}
::: column
<br>

@@

::: column
```{r mdisc-item}
#| fig-width:  4
#| fig-height: 4
mirt_item_coords |>
  arrange(desc(item))   |> # To plot them in reverse order
  ggplot(
    aes(
      0, 0,
      xend = end_transf_1 - origin_transf_1,
      yend = end_transf_2 - origin_transf_2,
      color = factor(item), fill = factor(item)
    ),
  )                                                  +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
  geom_hline(yintercept = 0, linewidth = LINE_WIDTH) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  ) +
  scale_x_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_y_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_color_manual(values = unname(PALETTE_BLUE["normal"]), guide = NULL) +
  coord_fixed(expand = FALSE, clip = "on")           +
  theme(
    axis.line        = element_blank(),
    panel.grid.major = element_line(
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```
:::
:::::
